---
title: "Reliability Intraoral Scanner"
output: html_notebook
---
# Packages

```{r packages}
library(tidyverse)
library(janitor)
library(irr)
```

```{r create df}
df <- readxl::read_xlsx("reliability_data.xlsx", sheet = "Sheet2" )

```

Clean names and empty cols
```{r clean names}
df <- df  %>% 
        janitor::clean_names() %>% 
        janitor::remove_empty_cols()



```

Create two datasets, for min and max

```{r two datasets}

min <- df %>% 
        select(min:d_21_l) %>% 
        mutate(type = "comparison") %>% 
        gather(d_13_d:d_21_l, key = "tooth", value = "difference")
colnames(min)[colnames(min) == "min"] <- "comparison"


max <- df %>% 
        select(max:d_21_l_1) %>% 
        mutate(type = "comparison") %>% 
        gather(d_13_d_1:d_21_l_1, key = "tooth", value = "difference")
colnames(max)[colnames(max) == "max"] <- "comparison"

max$tooth = substr(max$tooth,1,nchar(max$tooth) -2)

```

Join datasets

```{r bind}
df2 <- bind_rows(min, max) #create a semi tidy dataset
df2 <- df2 %>% 
        select(-type)
```

```{r delete old datasets}
# rm(df, min, max) #delete unused datasets
```
#Descriptive stats

```{r}
df2 %>% 
        select(comparison:difference) %>% 
        group_by(comparison) %>% 
        summarise_each (funs(min, 
                      q25 = quantile(., 0.25), 
                      median = median, 
                      q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd), 
                      difference)

```



abs difference
```{r mutate abs diff y expect diff}
df2 <- df2 %>% 
        mutate("abs_diff" = abs(difference)) #absolute difference

df2 <- df2 %>% 
        mutate("expect_diff" = 0) #expected difference = 0

```

# Distribution
```{r histogram}
df2 %>% 
        ggplot(aes(x = abs_diff)) +
        geom_histogram(bins = 5) + 
        scale_x_log10()
```
There is an outlier

```{r locate outliers}
which.max(df2$abs_diff)
```
Delete the outlier

```{r delete outlier}
df2 <- df2[-830, ]
```

```{r}
df2 %>% ggplot(aes(difference)) + 
        geom_histogram(bins = 10) + 
        labs(title = "Distribution of the differences between measurements", 
             x = "Difference", 
             y = "Counts") + 
        theme_minimal()
```


```{r df3 matrix}
df3 <- df2 %>% 
        group_by(tooth, comparison) %>% 
        summarise("Average" = mean(difference)) %>% 
        spread(comparison, value = Average)



```





# Agreement
```{r icc}
df3 %>% 
        ungroup() %>% 
        select(1--10:9--10) %>% 
        icc(., model = "twoway", type = "agreement")

```

There are significant differences between the measurements across raters

Absolute values matrix
```{r}
df3_abs <- df3 %>% 
        ungroup() %>% 
        select(1--10:9--10) %>% 
        abs(.) 

```

```{r}
df2 %>% 
        ggplot(aes(x = tooth, y = abs_diff)) +
        
        geom_boxplot() + 
        geom_jitter(alpha = 0.1) + 
        coord_flip() +
        labs( title = "Measurements per sample", 
              y = "Absolute difference", 
              x = "Sample and surface") + 
        theme_minimal()
```

Seems that the machine has some thresholds for detection, since there are no 0.01


```{r}
set.seed(3000)
df2 <- df2 %>% 
        mutate(expected_values = rnorm(1079, mean = 0, sd = 0.01))
```

```{r}
df2 %>% 
        select(difference, expected_values) %>% 
        gather("type", "value", 1:2) %>% 
        ggplot(aes(value, fill = type)) +
        geom_density(alpha = 0.4) + 
        labs(title = "Expected random variance vs real differences", 
             subtitle = "3 samples, 4 measurements each.", 
             x = "Difference", 
             y = "Count", 
             fill = "Key") + 
        theme_minimal()
```


```{r}
df2 %>% 
        ggplot(aes(x = difference, y = expected_values)) +
        geom_point() +
        stat_smooth() + 
        labs(title = "Scatterplot expected vs real differences", 
             y = "Expected by random", 
             x = "Real differences") +
        theme_minimal()
```


```{r}
library(BlandAltmanLeh)

ba_plot <- bland.altman.plot(df2$difference, df2$expected_values, graph.sys="ggplot2", conf.int=.95)
ba_plot + theme_minimal() + 
        labs(title = "Altman-Bland plot", 
             subtitle = "Expected vs real differences", 
             y = "Difference expected - real", 
             x = "Mean of measurements")
```

# Is any statistical difference between expected and real differences?
## Against expected distribution
```{r}
t.test(df2$difference, df2$expected_values)
```

```{r}
df2 %>% 
        select(difference, expected_values) %>% 
        gather() %>% 
        ggplot(aes(x = key, y = value)) + 
        geom_boxplot() + 
        theme_minimal()
```


## As one sample
```{r}
t.test(df2$difference, mu = 0)
```

Are normally distributed the differences?

```{r}
shapiro.test(df2$difference)
```

```{r}
install.packages("ggpubr")
library("ggpubr")
ggqqplot(df2$difference, 
         ylab = "Measured differences",
         ggtheme = theme_minimal())
```
Compare with expected values
```{r}
ggqqplot(df2$expected_values, 
         ylab = "Expected values",
         ggtheme = theme_minimal())
```

```{r}
shapiro.test(df2$expected_values)
```
